Figures to insert in text

### 2018-03-05 Chapters/Chapter02.tex
Info-Theory stuff

\chapter{Results (vi): Information theoretical write operation}

@@

Consider the following. Given any two $n$-sized bitstrings, the probability of a Hamming distance $d$ is given by,

%\begin{align*}

$p(H=d)=\frac{ \binom{n}{d} }{ 2^n },$ \\

$p(H\leq d)={\frac{1}{2^n}}{\displaystyle\sum_{i=0}^{d}{\binom{n}{i}}  }$, \\

%\end{align}

@@

$p(H\geq n-d)={\frac{1}{2^n}}{\displaystyle\sum_{i=n-d}^{n}{\binom{n}{i}}  }$, \\
$p(d+1 \leq H \leq n-d-1)=2^n - {\frac{1}{2^{n-1}}}{\displaystyle\sum_{i=0}^{d}{\binom{n}{i}}  .}$ \\

accordingly, we have tested how SDM behaves when write weights are calculated using the amount of information given by each bitstring, i.e., $w(d) = -\log_2 \left( 2^{-n} \binom{n}{d} \right) = n - \log_2 \binom{n}{d}$, as in information theory \citep{cover2012elements}.

>>>>

\chapter{Results (vi): Information-theoretical write operation}

\begin{figure}[h!]
  \centering
  \subfloat[$w(d), d \in \{ 1, 2, ..., n\}.$]{\includegraphics[width=3.2in]{./images02/new-images/Info-theory-a-global.jpeg}}

  \subfloat[$w(d)$ for the desired range. ]{\includegraphics[width=3.2in]{./images02/new-images/Info-theory-b-to-500.jpeg}}

  \subfloat[stepwise $\left \lfloor{w(d)}\right \rfloor$ for fast integer computation.]{\includegraphics[width=3.2in]{./images02/new-images/Info-theory-c-stepwise.jpeg}}

  \caption{Computing the amount of information of a signal to each hard location in its access radius. (a) entirety of the space; (b) region of interest; (c) Fast computation is possible through a stepwise function. }
  \label{fig:info-theory-hypothesis}
\end{figure}

\begin{figure}[h!]
  \centering
  \subfloat[$w(d), d \in \{ 1, 2, ..., n\}.$]{\includegraphics[width=3.2in]{./images02/new-images/Info-theory-a-sum.jpeg}}

  \subfloat[$w(d)$ for the desired range. ]{\includegraphics[width=3.2in]{./images02/new-images/Info-theory-b-sum-range.jpeg}}

  \subfloat[stepwise $\left \lfloor{w(d)}\right \rfloor$ for fast integer computation.]{\includegraphics[width=3.2in]{./images02/new-images/Info-theory-c-sum-stepwise.jpeg}}

  \caption{Computing the sum of low-likelihood signals. (a) entirety of the space; (b) region of interest; (c) Fast computation through a stepwise function. }
  \label{fig:info-theory-sum-hypothesis}
\end{figure}

@@

Consider the following. Information Theory \citep{cover2012elements} let us compute the precise amount of information in an event, when given its probability $p$, through the measure of \emph{self-information}:\\

$I(p)= -log_2(p).$ \\

Now, given any two $n$-sized bitstrings, the probability of their Hamming distance being $d$ is given by,

$p(H=d)= {2^{-n} \binom{n}{d} } ,$ \\

$p(H\leq d)= 2^{-n} {\displaystyle\sum_{i=0}^{d}{\binom{n}{i}}}  $, \\

@@

$p(H\geq n-d)=2^{-n}{\displaystyle\sum_{i=n-d}^{n}{\binom{n}{i}}  }$, \\

$p(d+1 \leq H \leq n-d-1)=2^n - 2^{1-n}{\displaystyle\sum_{i=0}^{d}{\binom{n}{i}}, \forall d<n/2}$. \\

Hence the weighted write would, on each hard location, sum (or subtract) the following:  \\

$w(d) = -\log_2 \left( 2^{-n} \binom{n}{d} \right) = n - \log_2 \binom{n}{d}$, as seen in Figure \ref{fig:info-theory-hypothesis}.

It is easy to interpret this data though a binary tree approach.  How many binary questions would be needed to precisely define a bitstring?

  INTERPRET PLUS FIG

Another possibility would be to use the sum of all distances closer (and less likely) locations within $w(d)$,

$w(d) = -\log_2 \left( 2^{-n} \displaystyle\sum_{i=0}^{d}{\binom{n}{i}} \right) = n - \log_2 \displaystyle\sum_{i=0}^{d}{\binom{n}{i}}$, \\

This can be seen in \ref{fig:info-theory-sum-hypothesis}.
